## Regression Models - Final Prject

### Load data and check variables available 

We load the data from R package (mtcars) and summarize the data. There are 11 variables total, one of this if the oucome of interest "mpg" and the rest are our potential predictos.

``` {r setoptions, echo=TRUE}
  require(knitr)
library(datasets)
data(mtcars)
summary(mtcars)
names(mtcars)
```

### Look for any potential relation between variables

In order to visualize a relation between mpg and predictors: 1) boxplot, to see the distribution of predictos; and 2) scatter plot, to visualize potential relation 

``` {r}
  require(knitr)
par(mfrow = c(1, 2))
with(mtcars, boxplot(mpg/10, disp/50, hp/50, drat, wt, qsec/5, main = "Boxplots - distribution of predictos"), 
    xlab = "", ylab = "")
axisnames <- c("MPG/10", "DISP/50", "HP/50", "drat", "wt", "qsec/5")
axis(1, at = c(1, 2, 3, 4, 5, 6), labels = axisnames, las = 2, cex.axis = 0.9, 
    tck = -0.01)
pairs(mtcars)
```

Clearly, we can visualize some relation (positive or negative) between outcome and predictors.

### Regression model of transmission on fuel efficiency

The regression model is estimated as follows:
``` {r}
  require(knitr)
mtcarsmodel1 <- lm(mpg ~ am, data = mtcars)
summary(mtcarsmodel1)
```


The R square resuls show that that automatic transmission explains 36% of the variance in fuel consumption. The intercept shows the mean value of mpg. In both case, the intercept and the predictor as statistical significant. 

More imporant, the coefficient of am show the difference in means between the two groups. 
This means, that the diffrence in means between autotransmission (am=1) and (am=0) is positive (7.245)and significant. 

##APPENDIX - additional data displays

``` {r}
  require(knitr)
data(mtcars)
with(mtcars, table(cyl))
with(mtcars, table(am))
with(mtcars, table(gear))
with(mtcars, table(carb))
with(mtcars, table(vs))
par(mfrow = c(2, 2))
plot(mtcarsmodel1)
```